Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-30 paper/paper.tex
Notation

% Maths operators
\newcommand{\paths}{\operatorname{paths}}
\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
\newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }
\newcommand{\lesspreceq}[1]{\prescript{}{#1}{\preceq}\ }
\newcommand{\V}{\operatorname{V}}
\newcommand{\N}{\operatorname{N}}
\newcommand{\nds}{\operatorname{S}}
\newcommand{\loopcomp}[1]{\tset{\multimap}{#1}}

@@

A \emph{non-induced subgraph isomorphism} from a graph $P$ to a graph $T$ is an injective mapping $P
\rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An \emph{induced subgraph
isomorphism} $P \hookrightarrow T$ additionally maps non-adjacent vertices to non-adjacent vertices.
We define a \emph{$k$-less subgraph isomorphism} from $P$ to $T$ to be a subgraph isomorphism from all but
$k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P \lessnonind{k} T$ and $P
\lessind{k} T$ respectively. We write $p \lessmap{k} t$ to mean that the pattern vertex p is mapped
to the target vertex v.

@@

A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $\N(p) = \{ q \in \V(P) :
 p~\textnormal{and}~q~\textnormal{are adjacent}\}$ be the \emph{set of neighbours} of $p$.  The \emph{neighbourhood
degree sequence} (NDS) of $p$, $\nds(p)$, is the (non-ascending) sequence of degrees of its
neighbours.

@@

\begin{proposition}\label{prop:paths}
    Let $p,q \in \V(P)$ and $t,u\in \V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
     $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
\end{proposition}
\begin{proof}
Let $P_{2}$ be the set of all paths of length two between $p$ and $q$, \[P_{2} = \{((p,x),(x,q)) :
(p,x),(x,q)\in \operatorname{E}(P) \}\textnormal{.}\] As we are looking at paths of length 2,
the intermediate vertices lie in both neighbour vertex sets of $p$ and $q$. We can rewrite
$P_{2}$ as \[P_{2} = \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \}\textnormal{,}\] in
other words the intermediate vertices lie in the intersection of the neighbour sets of $p$ and
$q$, \[ P_{2}=\{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} \textnormal{.}\] Therefore
$\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.

>>>>

% Maths operators
\newcommand{\paths}{\operatorname{paths}}
\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
\newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }
\newcommand{\lesspreceq}[1]{\prescript{}{#1}{\preceq}\ }
\newcommand{\V}{\operatorname{V}}
\newcommand{\EdgeSet}{\operatorname{E}}
\newcommand{\N}{\operatorname{N}}
\newcommand{\nds}{\operatorname{S}}
\newcommand{\loopcomp}[1]{\tset{\multimap}{#1}}

@@

Throughout, our graphs are undirected, but may have loops.  We write $\V(G)$ for the vertex set of a
graph $G$, and $\EdgeSet(G)$ for its set of edges. We write $\N_G(v)$ for the \emph{neighbourhood}
of a vertex $v$ in $G$, and $v \sim_G w$ to mean $v$ is adjacent to $w$; where the graph is clear
from the context, the subscript is omitted.

A \emph{non-induced subgraph isomorphism} from a graph $P$ to a graph $T$ is an injective mapping
$\V(P) \rightarrowtail \V(T) $ which maps adjacent vertices to adjacent vertices. An \emph{induced subgraph
isomorphism} $P \hookrightarrow T$ additionally maps non-adjacent vertices to non-adjacent vertices.
We define a \emph{$k$-less subgraph isomorphism} from $P$ to $T$ to be a subgraph isomorphism from all but
$k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P \lessnonind{k} T$ and $P
\lessind{k} T$ respectively. We write $p \lessmap{k} t$ to mean that the pattern vertex p is mapped
to the target vertex v under either kind of mapping.

@@

The \emph{neighbourhood degree sequence} (NDS) of a vertex $p$, $\nds(p)$, is the (non-ascending)
sequence of degrees of its neighbours.

@@

\begin{proposition}\label{prop:paths}
    Let $p,q \in \V(P)$ and $t,u\in \V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
     $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
\end{proposition}
\begin{proof}
Let $P_{2}$ be the set of all paths of length two between $p$ and $q$, \[P_{2} = \{((p,x),(x,q)) :
(p,x),(x,q)\in \EdgeSet(P) \}\textnormal{.}\] As we are looking at paths of length 2,
the intermediate vertices lie in both neighbour vertex sets of $p$ and $q$. We can rewrite
$P_{2}$ as \[P_{2} = \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \}\textnormal{,}\] in
other words the intermediate vertices lie in the intersection of the neighbour sets of $p$ and
$q$, \[ P_{2}=\{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} \textnormal{.}\] Therefore
$\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.
